The Leaky Semicolon (Supplementary Material)

### 2021-12-30 paper/intro.tex
another typo

For optimized concurrent languages, it is surprising difficult to define a
model that allows common compiler optimizations and hardware reorderings yet
disallows nonsense behaviors that don't arise in practice.  The latter are
commonly known as ``thin-air'' behaviors \cite{DBLP:conf/esop/BattyMNPS15}.
There are only a handful of solutions, and all have deficiencies.  These can
be classified by their approach to dependency tracking (from strongest to
weakest):
\begin{itemize}
\item Syntactic dependencies
  \cite{DBLP:conf/pldi/LahavVKHD17,Boehm:2014:OGA:2618128.2618134,DBLP:conf/oopsla/VafeiadisN13,DBLP:journals/corr/abs-1804-04214}.
  These models require inefficient implementation of relaxed access.  This is
  a non-starter for safe languages like Java and JavaScript, and may be an
  unacceptable cost for low-level languages like \cXI{}.
\item Semantic dependencies \cite{Manson:2005:JMM:1047659.1040336,DBLP:conf/esop/JagadeesanPR10,DBLP:conf/popl/KangHLVD17,DBLP:journals/pacmpl/ChakrabortyV19,DBLP:conf/pldi/LeeCPCHLV20,promising-ldrf}. These models compute
  dependencies operationally using alternate worlds, making it impossible to
  understood a single execution in isolation; they also allow executions that
  violate temporal reasoning (see \textsection\ref{sec:related}).
\item No dependencies, as in \cXI{} \cite{DBLP:conf/esop/BattyMNPS15} and
  JavaScript \cite{DBLP:journals/pacmpl/WattRP19}.  This allows thin-air
  executions.
\end{itemize}

>>>>

For optimized concurrent languages, it is surprising difficult to define a
model that allows common compiler optimizations and hardware reorderings yet
disallows nonsense behaviors that don't arise in practice.  The latter are
commonly known as ``thin-air'' behaviors \cite{DBLP:conf/esop/BattyMNPS15}.
There are only a handful of solutions, and all have deficiencies.  These can
be classified by their approach to dependency tracking (from strongest to
weakest):
\begin{itemize}
\item Syntactic dependencies
  \cite{DBLP:conf/pldi/LahavVKHD17,Boehm:2014:OGA:2618128.2618134,DBLP:conf/oopsla/VafeiadisN13,DBLP:journals/corr/abs-1804-04214}.
  These models require inefficient implementation of relaxed access.  This is
  a non-starter for safe languages like Java and JavaScript, and may be an
  unacceptable cost for low-level languages like \cXI{}.
\item Semantic dependencies \cite{Manson:2005:JMM:1047659.1040336,DBLP:conf/esop/JagadeesanPR10,DBLP:conf/popl/KangHLVD17,DBLP:journals/pacmpl/ChakrabortyV19,DBLP:conf/pldi/LeeCPCHLV20,promising-ldrf}. These models compute
  dependencies operationally using alternate worlds, making it impossible to
  understand a single execution in isolation; they also allow executions that
  violate temporal reasoning (see \textsection\ref{sec:related}).
\item No dependencies, as in \cXI{} \cite{DBLP:conf/esop/BattyMNPS15} and
  JavaScript \cite{DBLP:journals/pacmpl/WattRP19}.  This allows thin-air
  executions.
\end{itemize}
